Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-03-01 manuscript/cpcrw_manuscript.Rmd
Added UGA methods
Based on 01-March-2016 email: We ran DOC on the water extract of the
soils by “Shimadzu 5000 TOC Analyzer”. The total carbon and nitrogen
were analyzed by an “Elementar Vario Max CNS” combustion analyzer.

The incubation experiment concluded on 9 December 2015, following the final CO~2~ and CH~4~ readings. Each soil core was maintained at the treatment-dependent temperature and moisture content (by mass) until removed for destructive sampling, December 14-18, 2015. Sub-samples were collected and composited throughout each soil core for dissolved organic carbon analysis (110 ± 24 g dry mass equivalent) and dry-mass calculations (~28 g each). The remaining core material was air-dried and separated into particles (>2 mm diameter) and soil (≤2 mm) using a U.S. Standard Test Sieve No. 10 (Fisherbrand,  Pittsburg, PA, USA). The dry mass and volume of soil were used in calculations of gravimetric and volumetric soil moisture content, respectively {Gardner, 1986 #4345}. Soil volume was caclulated as the total core volume minus the volume of particles >2 mm diameter, with the latter determined by water displacement. 
Air-dried soil and sub-samples stored at -20 °C were sent to the Agricultural and Environmental Services Laboratory at the University of Georgia Extension in February 2016 for total C, N, and dissolved organic C. Samples were combusted in an oxygen atmosphere at 1350 °C, converting elemental C and N into gaseous form. Infrared cells were then used to to determine C content, and a thermal conductivity cell to determine N. TODO: confirm UGA analytical methods and exact instruments.

>>>>

The incubation experiment concluded on 9 December 2015, following the final CO~2~ and CH~4~ readings. Each soil core was maintained at the treatment-dependent temperature and moisture content (by mass) until removed for destructive sampling, December 14-18, 2015. Sub-samples were collected and composited throughout each soil core for dissolved organic carbon analysis (110 ± 24 g dry mass equivalent) and dry-mass calculations (~28 g each). The remaining core material was air-dried and separated into particles (>2 mm diameter) and soil (≤2 mm) using a U.S. Standard Test Sieve No. 10 (Fisherbrand,  Pittsburg, PA, USA). The dry mass and volume of soil were used in calculations of gravimetric and volumetric soil moisture content, respectively {Gardner, 1986 #4345}. Soil volume was caclulated as the total core volume minus the volume of particles >2 mm diameter, with the latter determined by water displacement. Air-dried soil and sub-samples stored at -20 °C were sent to the Agricultural and Environmental Services Laboratory at the University of Georgia Extension in February 2016 for total C, N, and dissolved organic C. Samples were combusted in an oxygen atmosphere at 1350 °C, and measured for gaseous C and N using a Elementar Vario Max CNS. DOC was measured using a Shimadzu 5000 TOC Analyzer.
